---
title: "RcppMLPACK Easy Test"
author: "Aditya Samantaray"
output: html_document
---

# Easy Test

For an example for the kMeans function implemented in RcppMLPACK2, we'll use the trees and the wine datasets
## Including the libraries and dataset for this test
```{r echo= T, results='hide'}
library("data.table")
library("RcppMLPACK")
library("microbenchmark")
library("directlabels")
library("ggplot2")
library("dplyr")
data(wine, package = "rattle")
data(trees, package = "datasets")
```

Fitting the kMeans model with the RcppMLPACK package
```{r fitting}
kMeans(t(trees), 3)
wine$Type <- NULL
kMeans(t(wine), 4)
```
Now, we'll try to benchmark the RcppMLPACK kMeans implementation with the default kmeans implementation in R  
Note: kMeans() is the RcppMLPACK implementation whereas kmeans() is the default implementation in R  
For benchmarking, we'll use the microbenchmark package. It will run the functions 100 times and then provide us with the mean runtime.
```{r benchmark}
X <- wine
res <- data.frame()
for(i in 40:nrow(X))
{
  evaltime <- microbenchmark(kMeans(t(X), 3), kmeans(X, 3), times = 100L)
  res <- bind_rows(res, data.frame(i, list(summary(evaltime)[,c('min','mean','max')])))
}
res <- cbind.data.frame(c("MLPACK Kmeans", "R Kmeans"), res)
names(res) <- c("expr", names(res)[2:5])
p <- ggplot(res, aes(x = i))+
  #geom_ribbon(aes(ymin = min, ymax = max, fill = expr, group = expr), alpha = 1/2)+
  geom_line(aes(y = mean, group = expr, colour = expr))+
  ggtitle('Runtime(in milliseconds) vs Dataset Size') +
  xlab('Dataset Size') +
  ylab('Runtime (in milliseconds)')
direct.label(p,"angled.boxes")
```
Therefore, we see that the kMeans() method implemented in the RcppMLPACK package is much faster(twice the speed) on an average than the default implementation of kmeans() in R.